\documentclass[a4paper]{amsart}
\usepackage{mathtools}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\title{Estimation of media storage requirement}
\author{Gagarine Yaikhom}
\begin{document}
\maketitle

\section{Storage requirement for image tiling}

The following equation estimates for a single image file the total
storage requirement for maintaining a thumbnail and pre-generated
image tiles, in addition to the original image file.

$$
T = O + t + \lambda\times\sum_{i=0}^{|Z|}\ceil*{\frac{w \times z_i}{s}} \times \ceil*{\frac{h \times z_i}{s}}
$$

where,
\begin{table}[ht]
\begin{tabular}{rl}
$T$ & total space (in bytes) for storing original image, thumbnail and tiles,\\
$O$ & size of the original image (in bytes),\\
$t$ & size of a thumbnail (in bytes),\\
$w$ & width of the original image (in pixels),\\
$h$ & height of the original image (in pixels),\\
$s$ & width, or height, of a square tile (in pixels),\\
$\lambda$ & size of a square tile (in bytes),\\
$Z$ & set of zoom levels (in percentages) where $Z = \{z_i : z_i > 0 \textrm{ and } z_i \le 1\}$
\end{tabular}
\end{table}

\section{Estimation from sample data}

Based on sample image files that are representative of the data
submitted under TIFF, DICOM and BMP image formats, we have the
following sizes in bytes.

\begin{table}[ht]
\begin{tabular}{r|rrrrrrr}
  Type & Count & Min & 1st Quar. & Median & Mean & 3rd Quar. & Max\\\hline
  DCM & 662 & 4196872 & 4196882 & 4196978 & 4196950 & 4196980 & 4196990\\
  BMP & 416 & 2159674 & 2180154 & 2180154 & 2178776 & 2180154 & 2180154\\
  TIFF & 86 & 954558 & 1196091 & 1622273 & 1435718 & 1665202 & 1712686\\\hline
 & 1164 & 954558 & 2180154 & 4196876 & 3271669 & 4196980 & 4196990
\end{tabular}
\caption{File sizes by image type (requires thumbnails and tiles)}
\end{table}

\begin{table}[ht]
\begin{tabular}{r|rrrrrrr}
  Type & Count & Min & 1st Quar. & Median & Mean & 3rd Quar. & Max\\\hline
  PDF & 313 & 3748070 & 3749141 & 3749369 & 3749832 & 3749625 & 3869153
\end{tabular}
\caption{File sizes for other media (no thumbnails or tiles)}
\end{table}

\begin{table}[ht]
\begin{tabular}{rrrrrr}
Min & 1st Quar. & Median & Mean & 3rd Quar. & Max\\\hline
   5058 & 8132 & 8902 & 9377 & 9393 & 27274
\end{tabular}
\caption{Thumbnail sizes}
\end{table}

\begin{table}[ht]
\begin{tabular}{r|rrrrrr}
Tile width & Min & 1st Quar. & Median & Mean & 3rd Quar. & Max\\\hline
256 & 177 & 5246 & 8029 & 7361 & 9774 & 29081\\
128 & 165 & 1586 & 2250 & 2101 & 2705 & 8243
\end{tabular}
\caption{Tile sizes by tile width}
\end{table}

Based on the above statistics, and assuming that all of the submitted
image files do not deviate far off, we can estimate storage
requirements for thumbnails and $256\times 256$ image tiles using the
median values: $t = 8902$ and $\lambda = 8029$.

The following are representative storage requirements where we
pre-generate tiles for each of the zoom levels $Z =
\{0.1,0.25,0.5,0.75,1\}$. Since all of the thumbnails and tiles are in
the same common image format, JPEG in our case, we can use the same
values of $t$ and $\lambda$ for all image types.

\begin{table}[h]
\begin{tabular}{rrrr}
& DCM & BMP & TIFF\\\hline
$T$ & 4687620 & 2767144 & 2177147\\
$O$ & 4196978 & 2180154 & 1622273\\
$w$ & 2048 & 2048 & 1920\\
$h$ & 1024 & 1064 & 1168\\\hline
$e$ & 11\% & 22\% & 26\%
\end{tabular}
\end{table}

The value $e$ gives the percentage of total storage required for
storing the thumbnails and tiles. This value is directly proportional to the
number of tiles generated for each of the zoom levels, and therefore,
depends on $Z$.

\section{Recommendation}

Based on the conditions highlighted above, it would be safe to allocate
approximately 30\% extra space for tiles and thumbnails, assuming
image files do not deviate too far from the median. Nonetheless, if
the allocated space is insufficient, the tiling infrastructure allows
horizontal scaling using multiple image servers.

As to estimating the total storage required for storing all of the
original media data and the corresponding image tiles and thumbnails,
we have limited information to make a firm safe estimate. Nonetheless,
a rough estimate would be:

$$
R = 1.3 \times 4196876 \times l \times (b + m) \times p \times i
$$

where,
\begin{table}[h]
\begin{tabular}{rl}
$R$ & total space (in bytes) for storing original images, thumbnails and tiles,\\
$l$ & number of lines,\\
$b$ & number of baseline specimens per line,\\
$m$ & number of mutant specimens per line,\\
$p$ & number of media parameters in IMPReSS, and\\
$i$ & number of images per parameter.
\end{tabular}
\end{table}

Hence, assuming that we receive media data for 5000 lines ($l =
5000$), and that each line requires 7 males and 7 females ($m = 14$)
with twice as many baselines as mutants ($b = 28$), we would require
approximately \textbf{26 terabytes} of storage for all of the 25 media
parameters ($p = 25$) in IMPReSS, assuming each media parameter is
associated with only one image file ($i = 1$).

\textbf{Caveat:} Note here that since not all media parameters are
image files (e.g., PDF files), the actual storage requirement is
likely to be less than the estimated 26 terabytes. On the other hand,
we are not considering other image modalities such as 3D embryo data,
segmented or temporal image sets where $i > 1$.
\end{document}
